Paper Summary

### 2024-10-31 Paper_Summary.Rmd
Added Sargon's Assay 1 data analysis portion. Also modified the design of the plots to be more consistent.

```{r Assay 1: Figure 1a. Simulation & Analysis}
###Trait of Interest: Creating normally distributed female fly populations with average value corresponding to their average number of sexual interactions. Four populations corresponding to the 4 different combinations between female fly size and environment type. (small females in cages, small females in vials, large females in cages, large females in vials)

@@

# Create the bar graph with error bars (Environment on x-axis)
ggplot(data, aes(x = Environment, y = Mean, fill = Size)) + scale_y_continuous(breaks=c(0, 2, 4, 6, 8, 10)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, position = position_dodge(0.9)) +
  labs(
    title = "Random Graph Nonsense",
    x = '',
    y = "Average Number of Sexual Interactions in a 1 Minute Period",
    fill = ' ' 
  ) +
  theme_classic() +
  theme(
    legend.position = 'bottom',
    panel.border = element_rect(colour = 'black', fill = NA)
  ) +
  scale_fill_manual(values = c('#B6D0E2', '#F1E3D3'))  # Pastel blue and yellow for the legend
```

@@

#Creating useful variables to create the plot for Figure 1b.
MeanFeeding_Small<-c(10, 9)
MeanFeeding_Large<-c(6.5, 13.5)
EnvironmentType<-c('Vial', 'Cage')
x <- c(1, 2)
SD = c(1, 1, 1, 1)

plot(MeanFeeding_Small, axes=FALSE, xlab= "Mating Arena", ylab="Average Number of Feedings Observed", ylim = c(4, 16), pch = 15, col = '#B6D0E2', type = 'o', lwd = 2, cex = 1.5)
axis(2)
axis(1, at = seq_along(MeanFeeding_Small), labels = as.character(EnvironmentType), las = 0)
lines(c(1, 2), MeanFeeding_Large, col='#F1E3D3', pch = 17, type = 'o', lty = 2, lwd = 2, cex = 1.5)

@@

# Turn plot outline into a box to make it more cutesy
box()
```

>>>>

```{r Assay 1: Figure 1a. Simulation & Analysis}
# Trait of Interest:

@@

# Create the bar graph with error bars (Environment on x-axis)
ggplot(data, aes(x = Environment, y = Mean, fill = Size)) + scale_y_continuous(breaks=c(0, 2, 4, 6, 8, 10)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, position = position_dodge(0.9)) +
  labs(
    title = '(a)',
    x = '',
    y = "Average Number of Sexual Interactions in a 1 Minute Period",
    fill = ' ' 
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = 'bottom',
    panel.border = element_rect(colour = 'black', fill = NA)
  ) +
  scale_fill_manual(values = c('#B6D0E2', '#F1E3D3'))  # Pastel blue and yellow for the legend
```

@@

# Spawning and simulating useful variables to create the plot for Figure 1b
MeanFeeding_Small<-c(10, 9)
MeanFeeding_Large<-c(6.5, 13.5)
EnvironmentType<-c('Vial', 'Cage')
x <- c(1, 2)
SD = c(1, 1, 1, 1)

# Creating a plot that is similar to Figure 1b. in the paper
plot(MeanFeeding_Small, axes = FALSE, xlab= "Mating Arena", ylab="Average Number of Feedings Observed", ylim = c(4, 16), pch = 15, col = '#B6D0E2', type = 'o', lwd = 2, cex = 1.5)
  axis(2)
  axis(1, at = seq_along(MeanFeeding_Small), labels = as.character(EnvironmentType), las = 0)
  lines(c(1, 2), MeanFeeding_Large, col='#F1E3D3', pch = 17, type = 'o', lty = 2, lwd = 2, cex = 1.5)
  title(main = '(b)')

@@

  # Turn plot outline into a box to make it more cutesy
  box()
```
```{r Assay 2: Figure 2. Simulation & Analysis}
low.vial<-rnorm(35, 1, 0.1)
high.vial<-rnorm(35, 1, 0.1)
low.cage<-rnorm(35, 1, 0.1)
high.cage<-rnorm(35, 1, 0.1)
g<-sample(1:4, 140, replace=TRUE)
error<-ifelse(g==1, 0.1, ifelse(g==2, 0.5, 1.5))
g<-as.factor(g)
response<-24*low.vial+17*high.vial+30*low.cage+28*high.cage+rnorm(140, mean=0, sd=0.1)
data<-cbind.data.frame(response, low.vial, high.vial, low.cage, high.cage)
model1<-glm(response~low.vial+high.vial+low.cage+high.cage, data=data)
summary(model1)
anova(model1)
```
